Bayesian spectral density estimation using P-splines with quantile-based knot placement

### 2020-11-05 responses/responses3/response.tex

\response{We would like to thank the referee for a thorough review of our paper. Below, you find a point-by-point response to your points raised. We have now carefully revised the paper taking all of your -- and the other referee's -- comments into account and hope that you will now find the paper acceptable for publication. For your convenience, all changes made are marked in red in the manuscript.}

\textbf{Major comment:}

\refereeQuote{p.8, Quantile-based knot placement\\
I could not understand the meaning of ``calculate its distribution function $F_z = P(z \leq z_i)$" in the second item of the procedure.  The values of the transformed periodogram $z_i$ are regarded as the values of the density $\tilde{f}$, which is non-monotonic, taken at equally-spaced frequencies.  According to item 4, the distribution function $F_z$, and hence the density function $\tilde{f}$, should be defined on the frequency domain. \\
I had a look at the R codes of the package psplinePsd. I think that the density function $\tilde{f}$ is a linear spline that interpolates as
\begin{align*}
\tilde{f} \left(\dfrac{\lambda_k}{2\pi}\right) = \dfrac{z_k}{\sum_{i=1}^{\nu}z_i}, \quad k=1,\dots,\nu.
\end{align*}
}

\response{That's correct!  The $\widetilde{f}$ is actually a probability mass function (not a probability density function), which is interpolated.  However, we have simplified a bit our knot allocation algorithm avoiding that step.  The new version of the algorithm is described step by step in our manuscript.  This change led to small changes in our application section, which has been consequently updated.  We have also updated the \texttt{psplinePsd} package on GitHub.

We'd like to clarify that the knot allocation procedure is described in the frequency domain in our manuscript.  However, the functions in our R implementation are defined in the interval [0,1] for convenience.
}\bigskip

### 2020-11-05 pSplines.tex
update

{\pmr
The procedure for the frequencies in the unit interval $\omega_l = 2 l/n  \in[0,1]$, which can be easily translated to the frequency domain, can be summarized as follows:	
\begin{enumerate}
	\item Let $\bm{x} = \left (\sqrt{I_n(\pi\omega_1)}, \dots, \sqrt{I_n(\pi\omega_{\nu})} \right)$ be the square root of the periodogram values.
	\item Define $y_l = \left|\dfrac{x_l - \bar{x}}{S_x} \right|$ where $\bar{x}$ denotes the average and $S_x$ the standard deviation of ${\bm x}$.
	\item Define $z_l = \frac{y_l}{\sum_{l=1}^{\nu} y_l}$, $Z_l= \sum_{j\leq l} z_j$, and let $F$ denote the continuous cdf that interpolates the $Z_l$, $l=1,\ldots,\nu$.
	\item Let $\bm{q} =\left( q_1, \dots, q_{K^*} \right)$ be a vector of $K^*$ equally spaced points  in  $[0,1]$, that is $q_j = \frac{j-1}{K^*-1}$, for $j=1,\dots,K^*$.
	\item The Q-spaced internal knot vector is given by the corresponding quantiles $\bm{\xi}^* = \left(F^{-1}(q_1),\dots, F^{-1}(q_{K^*}) \right)$. %where the inverse function is obtained by interpolation.	
\end{enumerate}

>>>>

{\pmr
The procedure can be summarized as follows:	%for the frequencies in the unit interval $\omega_l = 2 l/n  \in[0,1]$, which can be easily translated to the frequency domain, can be summarized as follows:	
\begin{enumerate}
	\item Let $\bm{x} = \left (\sqrt{I_n(\lambda_1)}, \dots, \sqrt{I_n(\lambda_{\nu})} \right)$ be the square root of the periodogram values.
	\item Define $y_l = \left|\dfrac{x_l - \bar{x}}{S_x} \right|$, for $l=1,\ldots,\nu$, where $\bar{x}$ denotes the average and $S_x$ the standard deviation of ${\bm x}$.
	\item Define $z_l = \frac{y_l}{\sum_{l=1}^{\nu} y_l}$, $Z_l= \sum_{j\leq l} z_j$, and let $F$ denote the continuous cdf that interpolates the $Z_l$.
	\item Let $\bm{q} =\left( q_1, \dots, q_{K^*} \right)$ be a vector of $K^*$ equally spaced points  in  $[0,1]$, that is $q_j = \frac{j-1}{K^*-1}$, for $j=1,\dots,K^*$.
	\item The Q-spaced internal knot vector is given by the corresponding quantiles $\bm{\xi}^* = \left(F^{-1}(q_1),\dots, F^{-1}(q_{K^*}) \right)$. %where the inverse function is obtained by interpolation.	
\end{enumerate}
